\documentclass[margin,line]{res}
\usepackage{url}

\oddsidemargin -0.2in
\evensidemargin -0.2in
\textwidth=5.5in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{\huge Fu Li \vspace*{.2in}}



\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{4in}p{4in}}
{\it Homepage:}  \url{iiis.tsinghua.edu.cn/~RC3/fuli} \\
{\it E-mail:}  fuli.theory.research@gmail.com \\
{\it Mobile:}  +86-187 1011 2911 \\
%{\it Mail Address:} 7th Floor, Building A, Technology Fortune Center

\end{tabular}



\section{\sc Education}
{\bf Tsinghua University}, Beijing, China \hfill {\bf August, 2014 - now}\\
{\em Institute for Interdisciplinary Information Science}\\
\\
\vspace*{-.1in}
\begin{list1}
	\item[] Ph.D. Major: Computer Science and Technology 
	
\end{list1}



{\bf Tsinghua University}, Beijing, China \hfill {\bf August, 2010 - July, 2014}\\
{\em Institute for Interdisciplinary Information Science}\\
\vspace*{-.1in}
\begin{list1}
\item[] B.E.  Major: Computer Science and Technology 
\end{list1}

%{\bf Massachusetts Institute of Technology}, Cambridge, MA, USA \\
%\hspace*{\fill} {\bf January, 2013 - May, 2013}\\
%{\em Department of Electrical Engineering and Computer Science}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] CTCS Exchange Student
%\begin{list2}
%\vspace*{.05in}
%\item GPA:  5.0/5.0
%\item Courses: Information Theory, Quantum Information Science, Network and Computer Security
%\end{list2}
%\vspace*{.05in}
%\end{list1}

%{\bf  High School}, Tianjin, China \hfill {\bf September, 2007 - June, 2010}\\

\section{\sc Honors and Awards}

\begin{itemize}
  \item Tsinghua University Freshman Scholarship, Second Prize \hfill December, 2010
  \item China Mathematics Olympic (CMO), Gold Medal \hfill January, 2010
  \item Tsinghua Xuetang Talents Scholarship Program, Tsinghua University \hfill 2010 - 2014
\end{itemize}


\section{\sc  Publications and Preprints}


Wei Chen, {\bf Fu Li},  Tian Lin and Aviad Rubinstein. \textit{Combining Traditional Marketing and Viral Marketing with Amphibious Influence Maximization
}, in the \textit{16-th ACM Conference on Economics and Computation (EC'15)}: June 17-19, 2015


{\bf Fu Li}, Iddo Tzameret and Zhengyu Wang. \textit{ Non-Commutative Formulas and Frege Lower Bounds: A New Characterization of Propositional Proofs
}, in\textit{ Conference on Computational Complexity  (CCC)}, 2015


{\bf Fu Li} and Iddo Tzameret. \textit{Generating Matrix Identities and Proof Complexity}, Electronic Colloquium on Computational Complexity TR13-185. Submitted, 2014.




\section{\sc Research Experience}

{\bf Microsoft Software Research Asian}, Beijing, China \hfill {\bf April, 2014 - Present}\\
{\em Theory group}\\
\vspace*{-.1in}
\begin{list1}
	\begin{list2}
		\vspace*{.05in}
		\item Supervisor: Dr. Wei Chen
		\item Studied influence maximization problem  in social network
		and find its applications to marketing. Proved hardness results of approximation in randomized algorithm and deterministic algorithm. Analyzed sensitivity of influence spread function. Designed approximation algorithms of influence maximization for solving marketing problems. 
		
	\end{list2}
	
	\vspace*{.05in}
\end{list1}



{\bf Tsinghua University}, Beijing, China \\
\vspace*{-.1in}
\hspace*{\fill} {\bf April, 2012 - June, 2014}\\
{\em Institute for Interdisciplinary Information Science}\\
\vspace*{-.1in}
\begin{list1}
\item[] Research Practise
\begin{list2}
\vspace*{.05in}
\item Supervisor: Dr. Iddo Tzameret
%\item Project: Lower Bounds Questions in Proof Complexity
\item
Extensive two years research in computational complexity. Emphasis on algebraic techniques. Specifically, investigation on the limits of non-commutative computation  and study of non-commutativity in Proof Complexity.  Initiate new approaches for establishing super-polynomial lower bounds on the size of strong proof systems, which addresses fundamental questions in complexity theory.
\end{list2}
\vspace*{.05in}
\end{list1}

{\bf Tsinghua University}, Beijing, China \\
\vspace*{-.1in}
\hspace*{\fill} {\bf April 2011 - 2012}\\
{\em Department of Computer Science}\\
\vspace*{-.1in}
\begin{list1}
\item[] Student Research Training
\begin{list2}
\vspace*{.05in}
\item Supervisor: Dr. Baolin Liu
\item Project:  Cognitive Computation of Audio-Visual Information
\item Study the work pattern of human brain recognizing  texture. Design experiments to collect electroencephalograms when human recognize texture from given pictures. Computer aided analysis to discover patterns in electroencephalograms.
\end{list2}
\vspace*{.05in}
\end{list1}



\section{\sc Current Research Interests }
\begin{list2}
	\item Computational complexity, including algebraic complexity, complexity of proofs and circuits lower bounds;
	\item  Derandomization, Pseudorandomness, Randomness Extraction;
	\item Combinatorial optimization, and stochastic optimization.
\end{list2}
%

\section{\sc Languages and Skills}
\begin{list2}
	\item Languages:  Mandarin Chinese (native), English (fluent).
	\item Programming languages:  C/C++, Java, Ruby.
\end{list2}


%{\bf Massachusetts Institute of Technology}, Cambridge, MA, USA \\
%\hspace*{\fill} {\bf February, 2013 - May, 2013}\\
%{\em Laboratory for Information and Decision Systems}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Undergraduate Research Opportunity Program
%\begin{list2}
%\vspace*{.05in}
%\item Supervisor: Dr. Yury Polyanskiy
%\item Project: Fundamental Limits on Bit-Error-Rate for Repeated Small Codes in Joint-Source Channel Coding
%\end{list2}
%\vspace*{.05in}
%\end{list1}
%
%
%{\bf University of Waterloo}, Waterloo, ON, Canada \hfill {\bf June, 2013 - August, 2013}\\
%{\em Institute for Quantum Computing}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Research Assistant
%\begin{list2}
%\vspace*{.05in}
%\item Supervisor: Dr. Norbert L\"{u}tkenhaus
%\item Project: Research on Theoretical Limits of Experimental Quantum Key Distribution
%\item Attending the Quantum Key Distribution Summer School and QCrypt 2013.
%\end{list2}
%\vspace*{.05in}
%\end{list1}
%
%
%
%{\bf Massachusetts Institute of Technology}, Cambridge, MA, USA \\
%\hspace*{\fill} {\bf February, 2013 - May, 2013}\\
%{\em Media Lab}\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Undergraduate Research Opportunity Program
%\begin{list2}
%\vspace*{.05in}
%\item Student Tutor: Akane Sano
%\item Project: Prediction of Human Behavior Based on Motion Sensor's Data
%\end{list2}
%\vspace*{.05in}
%\end{list1}




\end{resume}

\end{document}




